---
title: "SciViews svDialogs, Tcl/Tk version"
author: "Philippe Grosjean (phgrosjean@sciviews.org)"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{SciViews svDialogs, Tcl/Tk version}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This package demonstrate how to reimplement the {svDialogs} functions using different widgets and GUI. Only a couple of dialog boxes are currently implementation, just for the sake of that demonstration.

**You should execute the code in this vignette in an R interactive session that supports Tcl/Tk display in order to get the various dialog boxes!**

```{r}
# This must be TRUE in order to see the Tcl/Tk dialog boxes
capabilities("tcltk")
```

When {svDialogs} is loaded, it creates a default `.GUI` object using `nativeGUI` (native dialog boxes) in priority, followed by textual versions at the command line as fallback alternative (`textCLI`).

```{r}
library(svGUI)
library(svDialogs)
# The default GUI
.GUI
def_widgets <- gui_widgets(.GUI)
def_widgets
```

This means that {svDialogs} will use a native box (or a text version, depending from where you run the code in R) for this code:

```{r, eval=FALSE}
dlg_message("Hello world!")$res
```

To use the Tcl/Tk dialog boxes implemented in {svDialogstcltk} in the default GUI without changing anything in the subsequent code that uses the dialog boxes, you just have to load this package before use:

```{r}
library(svDialogstcltk)
gui_widgets(.GUI)
```

A new item, `tcltkGUI`, is inserted at the first position of the `gui_widgets()` specification in the `.GUI` object. The consequence is the use of the corresponding methods, if they are defined for the `dlg_xxx()` functions. For instance, you should now get a Tcl/Tk version of a message box with the following code:

```{r, eval=FALSE}
dlg_message("Hello world!")$res
```

# Using Tcl/Tk dialog boxes in a custom GUI

The {svDialogs} logic allows to implement simultaneously various GUIs, with different features. For instance, you may be interested to implement a Tcl/Tk-only GUI side-by-side with native dialog boxes that are used for the rest of the R process. In this case, you must manually insert the GUI you want to use in the GUI object.

```{r}
# Restore nativeGUI + textual fallback for the default .GUI
gui_change('.GUI', widgets = def_widgets, reset = TRUE)

# Add a new GUI called myGUI
gui_add("myGUI")
myGUI
# Switch to Tcl/Tk version of the dialog boxes exclusively for myGUI
gui_change('myGUI', widgets = "tcltkGUI", reset = TRUE)
```

Now, with this configuration, all code that use the default GUI will display native dialog boxes. However, code using `myGUI` will always display the Tcl/Tk version of the dialog boxes.

```{r}
# A message box in the default GUI (native)
dlg_message("Hello from the default GUI!")$res

# A message box in myGUI (Tcl/Tk version)
dlg_message("Hello from myGUI (Tcl/Tk)!", gui = myGUI)$res
```
